An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
More or less completed the intro and conclusions

@@

\author{Rinse~Wester~and~Robert~de~Groote}

@@

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism.
  \todo{ref to thesis Rinse \cite{Wester15}}
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance.
  \todo{ref naar thesis Robert \cite{deGroote16}}
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

  \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}

  \todo[inline]{mention CLaSH \cite{Baaij10} as used for backend}

@@

  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties.}

@@

  \begin{figure}[h]
    \centering
    \includegraphics[width=2.5in]{screenshot.png}
    \caption{Screenshot of SDFkit}
    \label{fig:screenshot}
  \end{figure}

@@

  \todo[inline]{extend conclusion a bit with current state of project}

  \todo[inline]{Future work: Complete support for CSDF, hierarchy is design environment, multicore and GPU code generation}

>>>>

\newcommand{\clash}{C$\lambda$aSH}

@@

\author{Rinse~Wester~and~Robert~de~Groote \\CAES group, EEMCS\\ University of Twente\\ \{r.wester, robert.degroote\}@utwente.nl}

@@

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance~\cite{deGroote16}.
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

  \begin{itemize}
    \item computational structures: \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}
    \item CSDF graphs and transformations
    \item simulation
    \item hardware generation using \clash \cite{Baaij10}
  \end{itemize}

@@

  \todo[inline]{Robert, kun je hier wat vertellen over de transformaties van computational structures naar CSDF graphs en bijbehorende transformaties, inclusief voorbeeld}

@@

  \begin{figure}[h!]
    \centering
    \includegraphics[width=3in]{screenshot.png}
    \caption{Screenshot of SDFkit}
    \label{fig:screenshot}
  \end{figure}

@@

  As a proof of concept, an interactive simulation and hardware generation environment named SDFkit is being developed.
  Currently, SDFkit supports visualization and simulation of HSDF, SDF and CSDF graphs.
  Additionally, \clash code can be generated for HSDF graphs.

  The next step in development is to extend the hardware code generation with support for SDF and CSDF graphs.
  Additionally, the transformations to make a tradeoff between space and time are now performed outside SDFkit.
  Integration of these transformations into SDFkit is therefore an other important step forward.
  Finally, Interesting opportunities lie in extending the backend with a wider range of supported platform like C code and OpenCL.
